\Title

### 2021-07-01 manuscript/content.tex
Simplify caption of the synthetic data

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
    \caption{
        Maps of the observation locations and gravity values for the synthetic
        ground and airborne surveys.
        (a)~Horizontal position and height of the ground survey points.
        (b)~Synthetic gravity data calculated on the ground survey points with
        added pseudo-random Gaussian noise.
        (c)~Horizontal position and height of the airborne survey points.
        (d)~Synthetic gravity data calculated on the airborne survey points
        with added pseudo-random Gaussian noise.
        Heights are given in meters above the zero height plane.
    }
    \label{fig:synthetic-layouts}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
    \caption{
        Observation heights and gravity values for the synthetic ground (a-b)
        and airborne (c-d) surveys.
        Heights are given in meters above the zero height plane.
        The synthetic gravity data are contaminated with pseudo-random Gaussian
        noise with zero mean and \SurveyNoise{} standard deviation.
    }
    \label{fig:synthetic-layouts}
\end{figure*}
